---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# semID

<!-- badges: start -->

[![R-CMD-check](https://github.com/zacharyvig/semID/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zacharyvig/semID/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

semID allows the user to input a Structural Equation Model (SEM) in `lavaan` syntax and check it against a number of identification rules from the literature.
Rules are specified as being necessary and/or sufficient and specific reasons are given when a rule is broken. Caution is given to the user in using the output
of the package as the sole determinant of model identification -- instead, it should be used as a "quick check" for any outstanding issues with the model.

## Installation

You can install the development version of semID from
[GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
# devtools::install_github("zacharyvig/semID")
```

## Example

``` {r}
library(semID)

# Holzinger and Swineford (1939) example
HS.model <- ' visual  =~ x1 + x2 + x3
              textual =~ x4 + x5 + x6
              speed   =~ x7 + x8 + x9 '
id(HS.model, warn = TRUE, call = "cfa", meanstructure = FALSE)
```
